\chapter*{{\color{oiB}Preface}\vspace{-6mm}}

\noindent%
\emph{Advanced High School Statistics} covers a first course in statistics, providing an introduction to applied statistics that is clear, concise, and accessible. This book was written to align with the AP$^{\text{\textregistered}}$ Statistics Course
Description\footnote{AP$^{\text{\textregistered}}$ is
  a trademark registered and owned by the College Board,
  which was not involved in the production of, and does
  not endorse, this product.
  \oiRedirect{collegeboard-ap_statistics_course_description}
      {apcentral.collegeboard.org/pdf/ap-statistics-course-description.pdf}}, but it's also popular in non-AP courses and community colleges.
\vspace{3mm}

\noindent%
This book may be downloaded as a free PDF at
\oiRedirect{ahss}{\color{black}\textbf{openintro.org/ahss}}.
\vspace{3mm}

\noindent%
We hope readers will take away three ideas from this book in addition to forming a foundation of statistical thinking and methods.\vspace{-1mm}
\begin{enumerate}
\setlength{\itemsep}{0mm}
\item[(1)] Statistics is an applied field with a wide range of practical applications.
\item[(2)] You don't have to be a math guru to learn from real, interesting data.
\item[(3)] Data are messy, and statistical tools are imperfect. But, when you understand the strengths and weaknesses of these tools, you can use them to learn about the real~world.
\end{enumerate}


\subsection*{{\color{oiB}Textbook overview}}

The chapters of this book are as follows:
\begin{description}
\setlength{\itemsep}{0mm}
\item[1. Data collection.] Data structures, variables, and basic data collection techniques; experimental designs and sampling methods are presented and compared.
\item[2. Summarizing data.] Data summaries and graphics;  includes normal approximation for data.
\item[3. Probability and probability distributions.] The basic principles of probability and random variables, as well as an introduction to the geometric and binomial distributions.
\item[4. Sampling distributions.] Sampling distributions for a sample proportion and a sample mean; also includes distributions for a difference of sample means and a difference of sample proportions.
\item[5. Foundations for inference.] General ideas for statistical inference in the context of estimating a population proportion.
\item[6. Inference for categorical data.]
    Inference for proportions and contingency tables
    using the normal and chi-square distributions.
\item[7. Inference for numerical data.]
    Inference for one or two sample means using the
    $t$-distribution.
\item[8. Introduction to linear regression.] An introduction to regression with two variables; includes inference on the slope of the regression line.
\end{description}

\subsection*{{\color{oiB}Online resources}}
OpenIntro is focused on increasing access to education by developing free,
high-quality education materials.
In addition to textbooks, we provide the following free resources
to help teachers and students be successful on our website.

\begin{itemize}
\setlength{\itemsep}{0mm}
\item Video overviews for each section of the textbook
\item Lecture slides for each section of the textbook
\item \oiRedirect{casio_all}{Casio} and \oiRedirect{ti_all}{TI} calculator tutorials
\item \oiRedirect{ahss-solutions}{Video solutions} for selected section and chapter exercises
\item Statistical software labs
\item A small but growing number of \oiRedirect{ahss-desmos}{Desmos activities}\footnote{\oiRedirect{ahss-desmos}{openintro.org/ahss/desmos}}
\item \oiRedirect{ahss-quizlet}{Quizlet} sets for each chapter\footnote{\oiRedirect{ahss-quizlet}{quizlet.com/openintro-ahss}}
\item A \oiRedirect{ahss-tableau}{Tableau public} page to further interact with data sets\footnote{\oiRedirect{ahss-tableau}{public.tableau.com/profile/openintro}}
%\item \oiRedirect{ahss2-online-temp}{Online, interactive version of textbook}\footnote{Developed by Emiliano Vega and Ralf Youtz of Portland Community College using PreTeXt.}
\item Complete companion course with the learning management software \oiRedirect{ahss_mom}{{MyOpenMath}}\footnote{\oiRedirect{myopenmath-ahss}{myopenmath.com/course/public.php?cid=11774}}
\item Complete Canvas course accessible through \oiRedirect{ahss_canvas}{{Canvas Commons}}\footnote{\oiRedirect{canvas_course-sfuhs}{sfuhs.instructure.com/courses/1068}}
\end{itemize}

\noindent%
All of these resources can be found at: 
\begin{center}
\oiRedirect{ahss}
    {\color{black}\textbf{openintro.org/ahss}}
\end{center}

\noindent%	
We also have improved the ability to access data in this book
through the addition of Appendix~\ref{appendix_data},
which provides additional information for each of the data sets
used in the main text.
Online guides to each of these data sets are also provided at
\oiRedirect{data}
    {\color{black}\textbf{openintro.org/data}}
and through a
\oiRedirect{textbook-github_openintro}
    {companion R~package}.

% Official:
% http://www.openintro.org/package/openintro
% Currently redirect it to:
% http://openintrostat.github.io/openintro-r-package/
\vspace{3mm}

\subsection*{{\color{oiB}Examples and exercises}}
%, and appendices}

\noindent%
Many examples are provided to establish an understanding of how
to apply methods.

\begin{examplewrap}
\begin{nexample}{This is an example.}
  Full solutions to examples are provided here, within the example.
\end{nexample}
\end{examplewrap}

\noindent%
When we think the reader should be ready to try an example problem
on their own, we frame it as Guided Practice.

\begin{exercisewrap}
\begin{nexercise}
The reader may check or learn the answer to any Guided Practice
problem by reviewing the full solution in a footnote.\footnotemark{}
%Readers are strongly encouraged to attempt these practice problems.
\end{nexercise}
\end{exercisewrap}
\footnotetext{Guided Practice solutions are always located down here!}

\noindent%
Exercises are also provided at the end of each section
and each chapter for practice or homework assignments.  
Solutions for odd-numbered exercises are given in
Appendix~\ref{eoceSolutions}.

\subsection*{{\color{oiB}Getting involved}}
We encourage anyone learning or teaching statistics to visit
\oiRedirect{textbook-openintro}
    {\color{black}\textbf{openintro.org}}
and get involved.
We~also value your feedback.
%Please send any questions or comments to \href{mailto:leah@openintro.org}{leah@openintro.org}.
Please provide feedback, report typos, and review known typos at
\begin{center}
\oiRedirect{ahss_feedback}
    {\color{black}\textbf{openintro.org/ahss/feedback}}
\end{center}


\subsection*{{\color{oiB}Acknowledgements}}

This project would not be possible without the passion
and dedication of all those involved.
The authors would like to thank the
\oiRedirect{textbook-openintro_about}{OpenIntro Staff}
for their involvement and ongoing contributions.
We~are also very grateful to the hundreds of students
and instructors who have provided us with valuable feedback
since we first started working on this project in~2009.
A special thank you to Stephen Miller and Juan Gomez for reviewing and providing feedback on the third edition of AHSS.




