\chapter{Data sets within the text}
\label{appendix_data}
\label{data_appendix}

%A foundational principle that supports quality statistical
%analysis is well-organized data.

\newcommand{\datawrap}[1]{#1 $\to$}
\newcommand{\seedataappendix}[1]{This data set
    is described in Data Appendix~\ref{#1}.}
\newcommand{\seedataappendixplural}[1]{These data sets
    are described in Data Appendix~\ref{#1}.}
\newcommand{\madeup}{This example was made up.}

\index{data|(}

Each data set within the text is described in this appendix.
For those data sets that are in multiple sections in a chapter,
only the first section is listed in that chapter.
If a data set is not listed here, e.g. Section~\ref{bayesTheoremSubsection}
lists imagined probabilities for whether a parking garage will
fill up and whether there is a sporting event that same evening
for an unnamed college, it may not be listed in this data appendix.
When a raw data set is available vs just a description,
there is a corresponding page for the data set at
\oiRedirect{data}
    {\color{black}\textbf{openintro.org/data}}.
That webpage also includes many more data sets than are
covered in this textbook,
and each data set on the website includes a description,
it's source, a detailed overview of each data set's variables,
and download options.



\datappendixch{Chapter 1:  \nameref{ch_data_collection}}

\begin{itemize}
\item[\ref{basicExampleOfStentsAndStrokes}]
   \datawrap{\datalink{stent30}, \datalink{stent365}}
    The stent data is split across two data sets,
    one for the 0-30 day and one for the 0-365 day results. \\
    Chimowitz MI, Lynn MJ, Derdeyn CP, et al. 2011.
    Stenting versus Aggressive Medical Therapy for
    Intracranial Arterial Stenosis.
    New England Journal of Medicine 365:993-1003.\\
    \oiRedirect{textbook-nejm_stent_study}
        {www.nejm.org/doi/full/10.1056/NEJMoa1105335}. \\
    NY Times article:
    \oiRedirect{textbook-nytimes_stent_study}
        {www.nytimes.com/2011/09/08/health/research/08stent.html}.

\item[\ref{dataBasics}]
    \datawrap{\datalink{loan50},
        \datalink{loans\_full\_schema}}
    This data comes from Lending Club
    (\oiRedirect{lendingclub-info-download-data}
        {lendingclub.com}),
    which provides a large set of data on the people who
    received loans through their platform.
    The data used in the textbook comes from a sample
    of the loans made in Q1 (Jan, Feb, March) 2018.
\item[\ref{dataBasics}]
    \datawrap{\datalink{county}, \datalink{county\_complete}}
    These data come from several government sources.
    For those variables included in the
    county data set, only the most recent data is reported,
    as of what was available in late 2018.
    Data prior to 2011 is all from
    \oiRedirect{census_gov}{census.gov},
    where the specific Quick Facts page providing the data
    is no longer available.
    The more recent data comes from
    \oiRedirect{ers_usda_gov-data_products-county_level_data_sets}
        {USDA (ers.usda.gov)},
    \oiRedirect{bls_gov-lau}
        {Bureau of Labor Statistics (bls.gov/lau)},
    \oiRedirect{census_gov-did-www-saipe}
        {SAIPE (census.gov/did/www/saipe)},
    and
    \oiRedirect{census_gov-programs_surveys-acs}
        {American Community Survey
            (census.gov/programs-surveys/acs)}.

\item[\ref{section_obs_data_sampling}]
    The study in mind regarding chocolate and heart attack patients:\\
    Janszky et al. 2009.
    \oiRedirect{textbook-2008_chocolate_health_study}
        {Chocolate consumption and mortality following
        a first acute myocardial infarction: the Stockholm
        Heart Epidemiology Program}.
    Journal of Internal Medicine 266:3, p248-257.

\item[\ref{section_obs_data_sampling}]
    The Nurses' Health Study was mentioned.
    For more information on this data set, see \\
    \oiRedirect{textbook-channing_nurse_study}
        {www.channing.harvard.edu/nhs}

\item[\ref{experimentsSection}]
    The study we had in mind during the introduction of
    Section~\ref{biasInHumanExperiments} was \\
    Anturane Reinfarction Trial Research Group. 1980.
    \emph{Sulfinpyrazone in the prevention of sudden
    death after myocardial infarction.}
    New England Journal of Medicine 302(5):250-256.
\end{itemize}




\D{\newpage}


\datappendixch{Chapter 2:  \nameref{ch_summarizing_data}}

\begin{itemize}

\item[\ref{numericalData}]
    \datawrap{\datalink{county}}
    This data set is described in
    the data for Chapter~\ref{ch_data_collection}.

\item[\ref{numericalData}]
    \datawrap{\datalink{email50}, \datalink{email}}
    These data represent emails sent to David Diez.
    Each data set includes 21~variables.
    The \datalink{email50} data set is a random sample
    of 50 emails from \datalink{email}.

\item[\ref{numericalSummariesAndBoxPlots}]
    \datawrap{\datalink{loan50}, \datalink{county}}
    These data sets are described in
    the data for Chapter~\ref{ch_data_collection}. \\
    \datawrap{\datalink{email50}, \datalink{email}}
    These data sets are described in
    the data for Section~\ref{numericalData}.

\item[\ref{numericalSummariesAndBoxPlots}]
    \datawrap{\datalink{possum}}
    The brushtail possum statistics are based on a sample
    of possums from Australia and New Guinea.
    The original source of this data is as follows:\\
    Lindenmayer DB, et al. 1995.
    \emph{Morphological variation among columns of the
        mountain brushtail possum, Trichosurus caninus
        Ogilby (Phalangeridae: Marsupiala)}.
    Australian Journal of Zoology 43: 449-458.

\item[\ref{normalDist}]
    \datawrap{SAT and ACT score distributions}
    The SAT score data comes from the 2018 distribution,
    which is provided at \\
    {\small
    \oiRedirect{textbook-collegeboard_sat_2018_score_distribution}
        {reports.collegeboard.org/pdf/2018-total-group-sat-suite-assessments-annual-report.pdf}} \\
    The ACT score data is available at \\
    {\footnotesize
    \oiRedirect{textbook-act_2018_score_distribution}
        {act.org/content/dam/act/unsecured/documents/cccr2018/P\_99\_999999\_N\_S\_N00\_ACT-GCPR\_National.pdf}} \\
    We also acknowledge that the actual ACT score distribution
    is \emph{not} nearly normal.
    However, since the topic is very accessible,
    we decided to keep the context and examples.

\item[\ref{normalDist}]
    \datawrap{\datalink{nba\_players\_19}}
    Summary information from the NBA players for the
    2018-2019 season.
    Data were retrieved from
   \oiRedirect{data-nba_players_19}{www.nba.com/players}.

%\item[\ref{normalDist}]
%    \datawrap{\datalink{possum}}
%    These data sets are described in
%    the data for Chapter~\ref{ch_summarizing_data}.

%\item[\ref{normalDist}]
%    \datawrap{\datalink{male\_heights\_fcid}}
%    This sample can be considered a simple random sample
%    from the US population.
%    It relies on the USDA Food Commodity Intake Database.
%\item[\ref{assessingNormal}]
%    \datawrap{\datalink{simulated\_normal}}
%    These data were simulated from a standard normal distribution.
%    This data set includes three different data sets.
%\item[\ref{normalDist}]
%    \datawrap{\datalink{poker}}
%    Poker winnings (and losses) for 50 days by a professional
%    poker player, which represents their first 50 days trying
%    to play for a living.
%    Anonymity has been requested by the player.
%\item[\ref{assessingNormal}]
%    \datawrap{\datalink{simulated\_dist}}
%    Simulated data sets,
%    not necessarily drawn from a normal distribution.
%    This data set includes six different data sets.

\item[\ref{categoricalData}]
    \datawrap{%\datalink{loan50},
        \datalink{loans\_full\_schema}}
    %\datawrap{\datalink{loan50}, \datalink{county}}
    This data set is described in
    the data for Chapter~\ref{ch_data_collection}.

\item[\ref{caseStudyMalariaVaccine}]
    \datawrap{\datalink{malaria}}
    Lyke et al. 2017.
    PfSPZ vaccine induces strain-transcending T cells
    and durable protection against heterologous controlled
    human malaria infection. \\
    PNAS 114(10):2711-2716.
 \oiRedirect{lyke-ishizuka-2017}
        {www.pnas.org/content/114/10/2711}
\end{itemize}




\datappendixch{Chapter 3:  \nameref{ch_probability}}

\begin{itemize}
\item[\ref{basicsOfProbability}]
    \datawrap{\datalink{email}}
    This data set is described in
    the data for Chapter~\ref{ch_summarizing_data}.
\item[\ref{basicsOfProbability}]
    \datawrap{\datalink{playing\_cards}}
    A table describing the 52 cards in a standard deck.
%\item[\ref{basicsOfProbability}]
%    \datawrap{\datalink{loan50}, \datalink{county}}
%    These data sets are described in
%    the data for Chapter~\ref{ch_data_collection}.

\item[\ref{conditionalProbabilitySection}]
    \datawrap{Machine learning on fashion.}
    This is a simulated data set, not based on
    any specific machine learning classifier.
\item[\ref{conditionalProbabilitySection}]
    \datawrap{\datalink{smallpox}}
    Fenner F. 1988.
    Smallpox and Its Eradication
    (History of International Public Health, No. 6).
    Geneva: World Health Organization. ISBN 92-4-156110-6.
\item[\ref{conditionalProbabilitySection}]
    \datawrap{\datalink{family\_college}}
    A simulated data set based on real population summaries at\\
    \oiRedirect{textbook-student_parent_college_2001}
        {nces.ed.gov/pubs2001/2001126.pdf}.

\item[\ref{conditionalProbabilitySection}]
    \datawrap{Mammogram screening, probabilities.}
    The probabilities reported were obtained using studies
    reported at
    \oiRedirect{textbook-breastCancerDotOrg_20090831b}
        {www.breastcancer.org}
    and \oiRedirect{textbook-ncbi_nih_breast_cancer}
        {www.ncbi.nlm.nih.gov/pmc/articles/PMC1173421}. 

\item[\ref{randomVariablesSection}]
    \datawrap{\datalink{stocks\_18}}
    Monthly returns for Caterpillar, Exxon Mobil Corp,
    and Google for November 2015 to October 2018.

\item[\ref{geomDist}]
    \datawrap{Blood type prevalence.}
    The fraction of people with O+ blood is about 38\% according to \\
    \oiRedirect{textbook-american_red_cross_o_positive_rate}
        {https://www.redcrossblood.org/donate-blood/blood-types/o-blood-type.html} \\
    We used 35\% for simplicity in the examples.

\end{itemize}


\D{\newpage}

\datappendixch{Chapter 4:  \nameref{ch_distributions}}

\begin{itemize}

\item[\ref{distributionphat}]
    \datawrap{Blood type prevalence.}
    This data set is described in
    the data for Chapter~\ref{ch_probability}.

\item[\ref{distributionofxbar}]
    \datawrap{\datalink{run17}, \datalink{run17samp}}
    These data set represent the full population and a sample
    of the runners and their run times in the 2017 Cherry Blossom Run
    in Washington, DC. For more details, see
    \oiRedirect{textbook-cherryblossom_org}{www.cherryblossom.org}.

\item[\ref{distributionofxbar}]
    \datawrap{\datalink{poker}}
    The full data set includes poker winnings (and losses)
    for 50 days by a professional
    poker player, which represents their first 50 days trying
    to play for a living.
    Anonymity has been requested by the player.

\end{itemize}



\datappendixch{Chapter 5:  \nameref{ch_foundations_for_inf}}

\begin{itemize}

\item[\ref{pointEstimates}]
    \datawrap{\datalink{email}}
    This data set is described in
    the data for Chapter~\ref{ch_summarizing_data}.

\item[\ref{pointEstimates}]
    \datawrap{\datalink{pew\_energy\_2018}}
    The actual data has more observations than were referenced
    in this chapter.
    That is, we used a subsample since it helped smooth some
    of the examples to have a bit more variability.
    The \data{pew\us{}energy\us{}2018} data set represents
    the full data set for each of the different energy source
    questions, which covers solar, wind, offshore drilling,
    hydrolic fracturing, and nuclear energy.
    The statistics used to construct the data are from
    the following page: \\
    \oiRedirect{textbook-pew_2018_poll_on_solar_and_wind_expansion}
        {{\small{www.pewinternet.org/2018/05/14/majorities-see-government-efforts-to-protect-the-environment-\\as-insufficient/}}}
    
\item[\ref{confidenceIntervals}]
    \datawrap{\datalink{pew\_energy\_2018}}
    See the details for this data set above
    in the Section~\ref{pointEstimates} data section.
\item[\ref{confidenceIntervals}]
    \datawrap{\datalink{ebola\_survey}}
    In New York City on October 23rd, 2014, a doctor who had
    recently been treating Ebola patients in Guinea went to
    the hospital with a slight fever and was subsequently
    diagnosed with Ebola.
    Soon thereafter, an NBC~4 New York/The Wall Street
    Journal/Marist Poll found that
    82\% of New Yorkers favored a
    ``mandatory 21-day quarantine for anyone who has come
    in contact with an Ebola patient''.
    This poll included responses of 1,042
    New York adults between Oct 26th and~28th, 2014.
    \oiRedirect{textbook-maristpoll_ebola_201410}
        {Poll ID NY141026 on maristpoll.marist.edu}.

\item[\ref{hypothesisTesting}]
    \datawrap{\datalink{transplant}}
    This is a made up data set about the health outcomes
    for a hypothetical medical consultant.
    Note that the data set on the website has 62 patients,
    not 142 patients, so there will a difference for what
    is covered in this book vs the data set on the website.

\end{itemize}



\datappendixch{Chapter 6:  \nameref{ch_inference_for_props}}

\begin{itemize}
%\item[\ref{singleProportion}]
%    \datawrap{Nuclear energy}
%    A Gallup poll of 1,019 adults in the US, conducted in March of 2016, found that 54\% of respondents oppose nuclear energy.  This was the first time since Gallup first asked the question in 1994 that a majority of respondents said they oppose nuclear energy.\\
%\oiRedirect{textbook-nuclear_energy_support_2016}
%        {https://news.gallup.com/poll/190064/first-time-majority-oppose-nuclear-energy.aspx}

\item[\ref{singleProportion}]
    \datawrap{Supreme Court}
    The Gallup organization began measuring the public's view of the Supreme Court's job performance in 2000, and has measured it every year since then with the question: ``Do you approve or disapprove of the way the Supreme Court is handling its job?".  In 2018, the Gallup poll randomly sampled 1,033 adults in the U.S. and found that 53\% of them approved. \\   
\oiRedirect{textbook-gallup_supreme_court_approval_2018}
        {https://news.gallup.com/poll/237269/supreme-court-approval-highest-2009.aspx}

\item[\ref{singleProportion}]
    \datawrap{Life on other planets}
    A February 2018 Marist Poll reported: ``Many Americans (68\%) think there is intelligent life on other planets".
    This is up from 52\% in 2005.
    The results were based on a random sample of 1,033 adults in the U.S. \\
\oiRedirect{textbook-intelligent_life_2018}{http://maristpoll.marist.edu/212-are-americans-poised-for-an-alien-invasion}

\item[\ref{singleProportion}]
    \datawrap{Congressional approval rating.}
    This survey data is from\\
    \oiRedirect{textbook-gallup_congress_2018}{news.gallup.com/poll/237176/snapshot-congressional-job-approval-july.aspx}

\item[\ref{singleProportion}]
    \datawrap{Tire inspection.}
    This is a hypothetical scenario not based on real data.

\item[\ref{singleProportion}]
    \datawrap{Toohey poll.}
    This is a hypothetical scenario not based on a real person
    or real data.

\item[\ref{singleProportion}]
    \datawrap{Support for nuclear energy.}
    The results are from the following Gallup poll:\\
    \oiRedirect{textbook-nuclear_energy_support_2016}{www.gallup.com/poll/182180/support-nuclear-energy.aspx}

\item[\ref{differenceOfTwoProportions}]
    \datawrap{\datalink{cpr}}
    B$\ddot{\text{o}}$ttiger et al.
    \emph{Efficacy and safety of thrombolytic therapy after
        initially unsuccessful cardiopulmonary resuscitation:
        a prospective clinical trial}.
        The Lancet, 2001.

\item[\ref{differenceOfTwoProportions}]
    \datawrap{\datalink{gear\_company}}
    This is a hypothetical scenario not based on real data.

\item[\ref{differenceOfTwoProportions}]
    \datawrap{\datalink{healthcare\_law\_survey}}
    Pew research survey on the Affordable Care Act (aka Obamacare)
    that ran the survey question with two variants.\\
    \oiRedirect{textbook-health_care_bill_2012}
        {http://www.people-press.org/2012/03/26/public-remains-split-on-health-care-bill-opposed-\\
        to-mandate/}

\item[\ref{differenceOfTwoProportions}]
    \datawrap{\datalink{fish\_oil\_18}}
    Manson JE, et al. 2018.
    Marine n-3 Fatty Acids and Prevention of
    Cardiovascular Disease and Cancer. NEJMoa1811403.

%\item[\ref{differenceOfTwoProportions}]
%    \datawrap{\datalink{mammogram}}
%    \oiRedirect{textbook-90k_mammogram_study_2014}
%        {Miller AB. 2014.
%            \emph{Twenty five year follow-up for breast cancer
%            incidence and mortality of the Canadian National
%            Breast Screening Study: randomised screening trial}.
%            BMJ 2014;348:g366.}

%\item[\ref{differenceOfTwoProportions}]
%    \datawrap{\datalink{drone\_blades}}
%    The quality control data set for quadcopter drone blades
%    is a made-up data set for an example.
%    We provide the simulated data in the
%    \data{drone\us{}blades} data set.

\item[\ref{oneWayChiSquare}]
    \datawrap{\datalink{jury}}
    Simulated data set of registered voter proportions
    and representation on juries from a population.

\item[\ref{oneWayChiSquare}]
    \datawrap{M\&Ms}
    Rick Wicklin collected a sample of 712 candies, or about 1.5 pounds,
    and counted how many there were of each color.   \\
\oiRedirect{textbook-mandms}{https://qz.com/918008/the-color-distribution-of-mms-as-determined-by-a-phd-in-statistics}

\item[\ref{twoWayTablesAndChiSquare}]
    \datawrap{\datalink{gsearch}}
    Simulated (fake) data set for Google search experiment.

\item[\ref{twoWayTablesAndChiSquare}]
    \datawrap{\datalink{ask}}
    Experiment results from asking about iPods, where the original source is:\\
    Minson JA, Ruedy NE, Schweitzer ME.
    \emph{There is such a thing as a stupid question:
    Question disclosure in strategic communication}. \\
    {\small\oiRedirect{minson_ruedy_data_source}
        {opim.wharton.upenn.edu/DPlab/papers/workingPapers/}}\\
    {\small\oiRedirect{minson_ruedy_data_source}
        {Minson\_working\_Ask\%20(the\%20Right\%20Way)\%20and\%20You\%20Shall\%20Receive.pdf}}

\item[\ref{twoWayTablesAndChiSquare}]
    \datawrap{Obama and Congressional approval by political affiliation.}
    This survey was completed by Pew Research and the full results
    may be found at:\\
    {\scriptsize\oiRedirect{textbook-obama_and_congress_approval_2012}{http://www.people-press.org/2012/03/14/romney-leads-gop-contest-trails-in-matchup-with-obama}}

%\item[\ref{twoWayTablesAndChiSquare}]
%    \datawrap{\datalink{diabetes2}}
%    Zeitler P, et al. 2012.
%    A Clinical Trial to Maintain Glycemic Control in Youth
%    with Type~2 Diabetes.
%    N Engl J Med.

\item[\ref{twoWayTablesAndChiSquare}]
    \datawrap{Attitudes on climate change}
    A Pew Research poll published in May of 2021 looks at how Americans’
    attitudes about climate change differ by generation, party and other factors.\\
    \oiRedirect{textbook-attitudes-climate-change}
      {\scriptsize{https://www.pewresearch.org/fact-tank/2021/05/26/key-findings-how-americans-attitudes-about-climate-change-differ-by-generation-party-and-other-factors/}}

\end{itemize}







\datappendixch{Chapter 7:  \nameref{ch_inference_for_means}}

\begin{itemize}
\item[\ref{oneSampleMeansWithTDistribution}]
    \datawrap{Risso's dolphins}
    Endo T and Haraguchi K. 2009.
    High mercury levels in hair samples from residents of Taiji,
    a Japanese whaling town.
    Marine Pollution Bulletin 60(5):743-747.

    Taiji was featured in the movie
    \emph{The Cove}, and it is a significant source of dolphin
    and whale meat in Japan.
    Thousands of dolphins pass through the Taiji area annually,
    and we will assume these 19 dolphins represent a simple
    random sample from those dolphins.
\item[\ref{oneSampleMeansWithTDistribution}]
    \datawrap{Croaker white fish}
    \oiRedirect{textbook-fda_mercury_in_fish_2010}
        {www.fda.gov/food/foodborneillnesscontaminants/metals/ucm115644.htm}

\item[\ref{oneSampleMeansWithTDistribution}]
    \datawrap{\datalink{run17samp}}
    This data set is described in
    the data for Chapter~\ref{ch_distributions}.

\item[\ref{pairedData}]
    \datawrap{\datalink{textbooks},
        \datalink{ucla\_textbooks\_f18}}
    Data were collected by OpenIntro staff in 2010 and again
    in 2018.
    For the 2018 sample, we sampled 201 UCLA courses.
    Of those, 68 required books could be
    found on Amazon.
    The websites where information was retrieved: \\
    \oiRedirect{ucla_class_schedule}
        {sa.ucla.edu/ro/public/soc},
    \oiRedirect{ucla_verbacompare}{ucla.verbacompare.com},
    and \oiRedirect{amazon}{amazon.com}.

\item[\ref{pairedData}]
    \datawrap{\datalink{sat\_improve}}
    This is a hypothetical (fake) data set for SAT improvement from
    an SAT preparation company.

\item[\ref{theTDistributionForTheDifferenceOfTwoMeans}]
    \datawrap{Jennifer-John study.}
    Bertrand M, Mullainathan S. 2004.
    \emph{Science faculty's subtle gender biases favor male students}.
    PNAS October 9, 2012 109 (41) 16474-16479.\\
    \oiRedirect{textbook-jennifer-john}
        {https://www.pnas.org/content/109/41/16474}

\item[\ref{theTDistributionForTheDifferenceOfTwoMeans}]
    \datawrap{\datalink{resume}}
    Study for racial bias in hiring, where the study's data is available
    in the \datalink{resume} data set.
    This data set is explored in great detail in the logistic regression
    section of the \oiRedirect{os}{OpenIntro Statistics} textbook.
    The original source for this data is:\\
    Bertrand M, Mullainathan S. 2004.
    \emph{Are Emily and Greg More Employable than Lakisha and Jamal?
    A Field Experiment on Labor Market Discrimination}.
    The American Economic Review 94:4 (991-1013).
    \oiRedirect{resume-data-2004}
        {www.nber.org/papers/w9873}

\item[\ref{theTDistributionForTheDifferenceOfTwoMeans}]
    \datawrap{Exams variants.}
    This is a simulated (fake) data set for exam performance
    of students for two different exam variations.

\item[\ref{theTDistributionForTheDifferenceOfTwoMeans}]
    \datawrap{\datalink{ncbirths}}
    A random sample of 1000 NC births.
    A sample of that random sample was used for the example
    in the section.

\item[\ref{theTDistributionForTheDifferenceOfTwoMeans}]
    \datawrap{\datalink{stem\_cells}}
        {Menard C, et al. 2005.
            Transplantation of cardiac-committed mouse embryonic
            stem cells to infarcted sheep myocardium:
            a preclinical study.
            The Lancet: 366:9490, p1005-1012.}
    \oiRedirect{textbook-menard_stem_cells_2005}{https://www.thelancet.com/journals/lancet/article/PIIS0140-6736(05)67380-1/fulltext}

\end{itemize}






\datappendixch{Chapter 8:  \nameref{ch_regr_simple_linear}}

\begin{itemize}
\item[\ref{fitting_line_to_data_section}]
    \datawrap{\datalink{simulated\_scatter}}
    Fake data used for the first three plots.
    The perfect linear plot uses group~4 data,
    where \var{group} variable in the data set
    (Figure~\ref{perfLinearModel}).
    The group of 3 imperfect linear plots use groups~1-3
    (Figure~\ref{imperfLinearModel}).
    The sinusoidal curve uses group~5 data
    (Figure~\ref{notGoodAtAllForALinearModel}).
        The group of 3 scatterplots with residual plots use groups~6-8
    (Figure~\ref{sampleLinesAndResPlots}).
    The correlation plots uses groups~9-19 data
    (Figures~\ref{posNegCorPlots} and~\ref{corForNonLinearPlots}).

\item[\ref{fitting_line_to_data_section}]
    \datawrap{\datalink{possum}}
    This data is described in
    the data for Chapter~\ref{ch_summarizing_data}.

\item[\ref{fitting_line_to_data_section}]
    \datawrap{\datalink{simulated\_scatter}}
    The plots for things that can go wrong uses groups 20-23
    (Figure~\ref{whatCanGoWrongWithLinearModel}).

\item[\ref{fittingALineByLSR}]
    \datawrap{\datalink{elmhurst}}
    These data were sampled from a table of data for all
    freshman from the 2011 class at Elmhurst College that
    accompanied an article titled
    \emph{What Students Really Pay to Go to College}
    published online by \emph{The~Chronicle of Higher Education}:
    \oiRedirect{textbook-chronicle_elmhurst_article}
        {chronicle.com/article/What-Students-Really-Pay-to-Go/131435}.

\item[\ref{fittingALineByLSR}]
    \datawrap{\datalink{textbooks},
        \datalink{ucla\_textbooks\_f18}}
    This data is described in
    the data for Chapter~\ref{ch_inference_for_means}.

\item[\ref{fittingALineByLSR}]
    \datawrap{\datalink{loan50}}
    This data set is described in
    the data for Chapter~\ref{ch_data_collection}.

\item[\ref{fittingALineByLSR}]
    \datawrap{\datalink{mariokart}}
    Auction data from Ebay (ebay.com) for the game Mario Kart
    for the Nintendo Wii.
    This data set was collected in early October, 2009.

\item[\ref{fittingALineByLSR}]
    \datawrap{\datalink{simulated\_scatter}}
    The plots for types of outliers uses groups 24-29
    (Figure~\ref{outlierPlots}).

\item[\ref{transformationForNonlinearData}]
  \datawrap{\datalink{county}, \datalink{county\_complete}}
    These data sets are described in
    the data for Chapter~\ref{ch_data_collection}.

\item[\ref{inferenceForLinearRegression}]
    \datawrap{\datalink{midterms\_house}}
    Data was retrieved from Wikipedia.

\end{itemize}


\index{data|)}

%\D{\newpage}

%This page is intentionally blank. If you are permitted to write in your textbook, write down a few statistics topics that are giving you trouble. Then write down what you will do to help fill in those knowledge gaps, such as working a few extra exercises, watching a few videos online to help clarify the topic(s), etc.
