\exercisesheader{}

% 25 - patreon_contributions_prob_dist

\eoce{\qt{Patreon contributions\label{patreon_contributions_prob_dist}}
The distribution of monthly contributions made to a particular
Patreon creator is given as follows:
\begin{center}
\begin{tabular}{lcccc}
\hline
Monthly Contribution & \$3 & \$5 & \$10 & \$25 \\
Proportion & 0.50 & 0.30 & 0.15 & 0.05 \\
\hline
\end{tabular}
\end{center}
\begin{parts}
\item Compute the average monthly contribution made to this creator.
\item Compute the standard deviation of the monthly contributions made to this creator.
\end{parts}
}{}

% 26 - experiment_launch_prob_dist

\eoce{\qt{Experiment launch impact\label{experiment_launch_prob_dist}}
An online shopping website develops new features and iterates on
its product recommendations on a regular basis.
The team also uses an experiment when launching each new feature
to assess the impact of the change on the total sales.
Below is a summary table of the impacts that the team observes:
\begin{center}
\begin{tabular}{lcccc}
\hline
Number of Sales From Launch & -200 & 0 & +200 & +500 \\
Proportion of Launches & 0.1 & 0.5 & 0.3 & 0.1 \\
\hline
\end{tabular}
\end{center}
\begin{parts}
\item Compute the average impact for the experiments.
\item Compute the standard deviation of the impact from these experiments.
\end{parts}
}{}

% 27 - hearts

\eoce{\qt{Hearts win\label{hearts}} In a new card game, you start
with a well-shuffled full deck and draw 3 cards without replacement.
If you draw 3 hearts, 
you win \$50. If you draw 3 black cards, you win \$25. For any other draws, you 
win nothing.
\begin{parts}
\item Create a probability model for the amount you win at this game, and find 
the expected winnings. Also compute the standard deviation of this distribution.
\item If the game costs \$5 to play, what would be the expected value and 
standard deviation of the net profit (or loss)? \textit{(Hint: 
profit = winnings $-$ cost; $X-5$)}
\item If the game costs \$5 to play, should you play this game? Explain.
\end{parts}
}{}

% 28 - ace_of_clubs

\eoce{\qt{Ace of clubs wins\label{ace_of_clubs}} Consider the following card game 
with a well-shuffled deck of cards. If you draw a red card, you win nothing. If 
you get a spade, you win \$5. For any club, you win \$10 plus an extra \$20 for 
the ace of clubs.
\begin{parts}
\item Create a probability model for the amount you win at this game. Also, find 
the expected winnings for a single game and the standard deviation of the 
winnings.
\item What is the maximum amount you would be willing to pay to play this game? 
Explain your reasoning.
\end{parts}
}{}

% 29 - portfolio_return

\eoce{\qt{Portfolio return\label{portfolio_return}} A portfolio's value increases 
by 18\% during a financial boom and by 9\% during normal times. It decreases by 
12\% during a recession. What is the expected return on this portfolio if each 
scenario is equally likely?
}{}

% 30 - baggage_fees

\eoce{\qt{Baggage fees\label{baggage_fees}} An airline charges the following 
baggage fees: \$25 for the first bag and \$35 for the second. Suppose 54\% of 
passengers have no checked luggage, 34\% have one piece of checked luggage and 
12\% have two pieces. We suppose a negligible portion of people check more than 
two bags.
\begin{parts}
\item Build a probability model, compute the average revenue per passenger, and 
compute the corresponding standard deviation.
\item About how much revenue should the airline expect for a flight of 120 
passengers? With what standard deviation? Note any assumptions you make and if 
you think they are justified.
\end{parts}
}{}
