\reviewexercisesheader{}

% 51 - grade_dists

\eoce{\qt{Grade distributions\label{grade_dists}} Each row in the table below is 
a proposed grade distribution for a class. Identify each as a valid or invalid 
probability distribution, and explain your reasoning.
\begin{center}
\begin{tabular}{l  ccccc} 
    & \multicolumn{5}{c}{\textit{Grades}} \\
\cline{2-6}
    & A     & B     & C     & D     & F  \\
\cline{2-6}
(a) & 0.3   & 0.3   & 0.3   & 0.2   & 0.1\\
(b) & 0     & 0     & 1     & 0     & 0 \\
(c) & 0.3   & 0.3   & 0.3   & 0     & 0 \\
(d) & 0.3   & 0.5   & 0.2   & 0.1   & -0.1 \\
(e) & 0.2   & 0.4   & 0.2   & 0.1   & 0.1 \\
(f) & 0     & -0.1  & 1.1   & 0     & 0 \\
\end{tabular}
\end{center}
}{}

% 52 - health_coverage_freqs

\eoce{\qt{Health coverage, frequencies\label{health_coverage_freqs}} The 
Behavioral Risk Factor Surveillance System (BRFSS) is an annual telephone survey 
designed to identify risk factors in the adult population and report emerging 
health trends. The following table summarizes two variables for the respondents: 
health status and health coverage, which describes whether each respondent had 
health insurance. \footfullcite{data:BRFSS2010}
\begin{center}
\begin{tabular}{rrrrrrrr}
                    &       & \multicolumn{5}{c}{\textit{Health Status}} &  \\ 
\cline{3-7}
                    &       & Excellent & Very good & Good  & Fair  & Poor  & Total\\ 
\cline{2-8}
\textit{Health}     & No    & 459       & 727       & 854   & 385   & 99    & 2,524 \\ 
\textit{Coverage}   & Yes   & 4,198     & 6,245     & 4,821 & 1,634 & 578   & 17,476 \\ 
\cline{2-8}
                    & Total & 4,657     & 6,972     & 5,675 & 2,019 & 677   & 20,000
\end{tabular}
\end{center}
\begin{parts}
\item If we draw one individual at random, what is the probability that the 
respondent has excellent health and doesn't have health coverage?
\item If we draw one individual at random, what is the probability that the 
respondent has excellent health or doesn't have health coverage?
\end{parts}
}{}

% 53 - tree_hiv_eswatini

\eoce{\qt{HIV in Eswatini\label{tree_hiv_eswatini}} Eswatini (formerly named in English as Swaziland) has the highest 
HIV prevalence in the world: 25.9\% of this country's population is infected with 
HIV.\footfullcite{ciaFactBookHIV:2012} The ELISA test is one of the first and 
most accurate tests for HIV. For those who carry HIV, the ELISA test is 99.7\% 
accurate. For those who do not carry HIV, the test is 92.6\% accurate. If an 
individual from Eswatini has tested positive, what is the probability that he 
carries HIV?
}{}

% 54 - tree_twins

\eoce{\qt{Twins\label{tree_twins}} About 30\% of human twins are identical, and 
the rest are fraternal. Identical twins are necessarily the same sex -- half are 
males and the other half are females. One-quarter of fraternal twins are both 
male, one-quarter both female, and one-half are mixes: one male, one female. You 
have just become a parent of twins and are told they are both girls. Given this 
information, what is the probability that they are identical?
}{}

% 55 - disjoint_indep

\eoce{\qt{Disjoint vs. independent\label{disjoint_indep}} In parts~(a) and~(b), 
identify whether the events are disjoint, independent, or neither (events cannot 
be both disjoint and independent).
\begin{parts}
\item You and a randomly selected student from your class both earn A's in this 
course. 
\item You and your class study partner both earn A's in this course.
\item If two events can occur at the same time, must they be dependent?
\end{parts}
}{}

% 56 - guessing_on_exam

\eoce{\qt{Guessing on an exam\label{guessing_on_exam}} In a multiple choice exam, 
there are 5 questions and 4 choices for each question (a, b, c, d). Nancy has not 
studied for the exam at all and decides to randomly guess the answers. What is 
the probability that:
\begin{parts}
\item the first question she gets right is the $5^{th}$ question?
\item she gets all of the questions right?
\item she gets at least one question right?
\end{parts}
}{}

\D{\newpage}

% 57 - edu_attain_parent_teen

\eoce{\qt{Educational attainment\label{edu_attain_parent_teen}} The \data{family\_\hspace{0.3mm}college} data set contains a sample of 792 cases with two variables, \var{teen} and \var{parents}, and is summarized below.\footnote{A simulated data set based on real population summaries at \oiRedirect{textbook-student_parent_college_2001}{nces.ed.gov/pubs2001/2001126.pdf}.} The \var{teen} variable is either \resp{college} or \resp{not}, where the \var{college} label means the teen went to college immediately after high school. The~\var{parents} variable takes the value \resp{degree} if at least one parent of the teenager completed a college degree.

\begin{table}[ht]
\centering
\begin{tabular}{ll rr r rr}
  && \multicolumn{2}{c}{\var{parents}} & \hspace{1cm} &  \\
  \cline{3-4}
	&& \resp{degree} & \resp{not} & Total  \\
  \cline{2-5}
	& \resp{college}     & 231 & 214 & 445 \\
\raisebox{1.5ex}[0pt]{\var{teen}}	& \resp{not} \hspace{0.5cm} & 49 & 298 & 347   \\
  \cline{2-5}
	& Total & 280 & 512 & 792 \\
\end{tabular}
\caption{Contingency table summarizing the \data{family\_\hspace{0.3mm}college} data set.}
\label{contTableOfParStCollege}
\end{table}
		
	\begin{parts}
		\item For a randomly selected case, what is the probability that a parent completed a college degree?
		\item For a randomly selected case, what is the probability that the teen went to college immediately after high school?
		\item For a randomly selected case, what is the probability that a parent completed a college degree \emph{and} teen went to college immediately after high school?  
		\item Is P(a parent completed college degree \emph{and} teen went to college immediately after high school) = P(parent completed college degree) x P(teen went to college immediately after high school)?  Explain why this is or is not the case.
	\end{parts}
}{}

% 58 - speeding_i5_intro

\eoce{\qt{Speeding on the I-5, Part I\label{speeding_i5_intro}} The distribution of 
passenger vehicle speeds traveling on the Interstate 5 Freeway (I-5) in 
California is nearly normal with a mean of 72.6 miles/hour and a standard 
deviation of 4.78 miles/hour.\footfullcite{Johnson+Murray:2010}
\begin{parts}
\item What percent of passenger vehicles travel slower than 80 miles/hour?
\item What percent of passenger vehicles travel between 60 and 80 miles/hour?
\item How fast do the fastest 5\% of passenger vehicles travel?
\item The speed limit on this stretch of the I-5 is 70 miles/hour. 
Approximate what percentage of the passenger vehicles travel above the speed 
limit on this stretch of the I-5.
\end{parts}
}{}

% 59 - college_smokers

\eoce{\qt{College smokers\label{college_smokers}} At a university, 13\% of 
students smoke.
\begin{parts}
\item Calculate the expected number of smokers in a random sample of 100 students 
from this university.
\item The university gym opens at 9 am on Saturday mornings. One Saturday morning 
at 8:55 am there are 27 students outside the gym waiting for it to open. Should 
you use the same approach from part (a) to calculate the expected number of 
smokers among these 27 students?
\end{parts}
}{}

% 60 - roulette_winnings

\eoce{\qt{Roulette winnings\label{roulette_winnings}} In the game of roulette, a 
wheel is spun and you place bets on where it will stop. One popular bet is 
that it will stop on a red slot; such a bet has an 18/38 chance of winning. 
If it stops on red, you double the money you bet. If not, you lose the money 
you bet. Suppose you play 3 times, each time with a \$1 bet. Let Y represent 
the total amount won or lost. Write a probability model for Y.
}{}

% 61 - mc_quiz

\eoce{\qt{Multiple choice quiz\label{mc_quiz}} In a multiple choice quiz there are 
5 questions and 4 choices for each question (a, b, c, d). Robin has not 
studied for the quiz at all, and decides to randomly guess the answers. What 
is the probability that
\begin{parts}
\item the first question she gets right is the $3^{rd}$ question?
\item she gets exactly 3 or exactly 4 questions right?
\item she gets the majority of the questions right?
\end{parts}
}{}

\D{\newpage}

% 62 - birth_weight

\eoce{\qt{Birth weight\label{birth_weight}}
In a large study of birth weight of newborns, the weights of 23,419 newborn boys were recorded. The distribution of weights was approximately normal with a mean of 7.44 lbs (3376 grams) and a standard deviation of 1.33 lbs (603 grams). The government classifies a newborn as having low birth weight if the weight is less than 5.5 pounds.\footnote{\oiRedirect{textbook-birthweight_for_Scottish_singleton_births}{www.biomedcentral.com/1471-2393/8/5}}
\begin{parts}
\item What percent of these newborns had a low birth weight?
\item Approximately what percent of these babies weighed greater than 10 pounds?
\item Approximately \emph{how many} of these newborns weighed greater than 10 pounds?
\item How much would a newborn have to weigh in order to be at the 90th percentile among this group?
\end{parts}
}{}

% 63 - auto_insurance_premiums

\eoce{\qt{Auto insurance premiums\label{auto_insurance_premiums}} Suppose a 
newspaper article states that the distribution of auto insurance premiums for 
residents of California is approximately normal with a mean of \$1,650. The 
article also states that 25\% of California residents pay more than \$1,800. 
\begin{parts}
\item What is the Z-score that corresponds to the top 25\% (or the $75^{th}$ 
percentile) of the standard normal distribution?
\item What is the mean insurance cost? What is the cutoff for the 75th 
percentile?
\item Identify the standard deviation of insurance premiums in California.
\end{parts}
}{}

% 64 - heights_10_yrs

\eoce{\qt{Heights of 10 year olds, Part I\label{heights_10_yrs}}
Heights of 10 year olds, regardless of gender, closely follow
a normal distribution with mean 55 inches and standard deviation
6~inches.
\begin{parts}
\item
    What is the probability that a randomly chosen 10 year old
    is shorter than 48 inches?
\item
    What is the probability that a randomly chosen 10 year old
    is between 60 and 65 inches?
\item
    If the tallest 10\% of the class is considered
    ``very tall'',
    what is the height cutoff for ``very tall"?
\end{parts}
}{}

% 65 - student_outfits

\eoce{\qt{Student outfits\label{student_outfits}} \videosolution{ahss_eoce_sol-student_outfits} In a classroom with 24 
students, 7 students are wearing jeans, 4 are wearing shorts, 8 are wearing 
skirts, and the rest are wearing leggings. If we randomly select 3 students 
without replacement, what is the probability that one of the selected students is 
wearing leggings and the other two are wearing jeans? Note that these are 
mutually exclusive clothing options.
}{}

% 66 - find_sd_cholesterol

\eoce{\qt{Find the SD\label{find_sd_cholesterol}}
Cholesterol levels for women aged 20 to 34 follow an
approximately normal distribution with mean 185 milligrams
per deciliter (mg/dl).
Women with cholesterol levels above 220 mg/dl are considered
to have high cholesterol and about 18.5\% of women fall into
this category.
What is the standard deviation of the 
distribution of cholesterol levels for women aged 20 to~34?
}{}
