\reviewexercisesheader{}

% 19 - university_admissions

\eoce{\qt{University admissions\label{university_admissions}} Suppose a university 
announced that it admitted 2,500 students for the following year's freshman 
class. However, the university has dorm room spots for only 1,786 freshman 
students. If there is a 70\% chance that an admitted student will decide to 
accept the offer and attend this university, what is the approximate 
probability that the university will not have enough dormitory room spots for 
the freshman class?
}{}

% 20 - sat_scores

\eoce{\qt{SAT scores\label{sat_scores}}
SAT scores (out of 1600) are distributed 
normally with a mean of 1100 and a standard deviation of 200.
Suppose a school council awards a certificate of excellence
to all students who score at least 1350 on the SAT,
and suppose we pick one of the recognized students at random.
What is the probability this student's score will be
at least 1500?
(The material covered in
Section~\ref{conditionalProbabilitySection} 
would be useful for this question.)
}{}

% 21 - overweight_baggage

\eoce{\qt{Overweight baggage\label{overweight_baggage}} Suppose weights of the 
checked baggage of airline passengers follow a nearly normal distribution 
with mean 45 pounds and standard deviation 3.2 pounds. Most airlines charge a 
fee for baggage that weigh in excess of 50 pounds. Determine what percent of 
airline passengers incur this fee.
}{}

% 22 - survey_response_rate

\eoce{\qt{Survey response rate\label{survey_response_rate}} Pew Research reported 
that the typical response rate to their surveys is only 9\%. If for a 
particular survey 15,000 households are contacted, what is the probability 
that at least 1,500 will agree to respond? \footfullcite{surveysPew}
}{}

% 23 - overweight_baggage_2

\eoce{\qt{Overweight baggage, Part II\label{overweight_baggage_2}} \videosolution{ahss_eoce_sol-overweight_baggage_part_II} Suppose weights of the checked baggage of airline passengers follow a nearly normal distribution with mean 45 pounds and standard deviation 3.2 pounds. What is the probability that the \emph{total} weight of 10 bags is greater than 460 lbs?
}{}

% 24 - chocolate_chip_cookies

\eoce{\qt{Chocolate chip cookies} Students are asked to count the number of chocolate chips in 22 cookies for a class activity. The packaging for these cookies claims that there are an average of 20 chocolate chips per cookie with a standard deviation of 4.37 chocolate chips.
\begin{parts}
\item Based on this information, about how much variability should they expect to see in the mean number of chocolate chips in random samples of 22 chocolate chip cookies?
\item What is the probability that a random sample of 22 cookies will have an average less than 14.77 chocolate chips if the company's claim on the packaging is true? Assume that the distribution of chocolate chips in these cookies is approximately normal.
\item Assume the students got 14.77 as the average in their sample of 22 cookies.  Do you have confidence or not in the company's claim that the true average is 20?  Explain your reasoning.
\end{parts}
}{}

% 25 - young_hispanics_2019

\eoce{\qt{Young Hispanics in the US\label{young_hispanics_2019}} The 2019 Current Population Survey (CPS) estimates that 36.0\% of the people of Hispanic origin in the Unites States are under 21 years old.\footfullcite{data:hispaniccps:2019} Calculate the probability that at least 35 people among a random sample of 100 Hispanic people living in the United States are under 21 years old.
}{}

% 26 - poverty_us_2019

\eoce{\qt{Poverty in the US\label{poverty_us_2019}} The 2019 Current Population Survey (CPS) estimates that 19.2\% of Mississippians live in poverty, which makes Mississippi the state with the highest poverty rate in the United States.\footfullcite{data:povertycps:2019} We are interested in finding out the probability that at least 200 people among a random sample of 1,000 Mississippians live in poverty.
\begin{parts}
\item Estimate this probability using the normal approximation to the binomial distribution.
\item Estimate this probability using the distribution of the sample proportion.
\item How do your answers from parts (a) and (b) compare?
\end{parts}
}{}

\D{\newpage}

This page is intentionally blank. 