\exercisesheader{}

% 1 - identify_parameter_1

\eoce{\qt{Identify the parameter, Part I\label{identify_parameter_1}} For each of the following situations, state 
whether the parameter of interest is a mean or a proportion. It may be helpful 
to examine whether individual responses are numerical or categorical.
\begin{parts}
\item In a survey, one hundred college students are asked how many hours per 
week they spend on the Internet.
\item In a survey, one hundred college students are asked: ``What percentage of 
the time you spend on the Internet is part of your course work?"
\item In a survey, one hundred college students are asked whether or not they 
cited information from Wikipedia in their papers.
\item In a survey, one hundred college students are asked what percentage of 
their total weekly spending is on alcoholic beverages.
\item In a sample of one hundred recent college graduates, it is found that 85 
percent expect to get a job within one year of their graduation date.
\end{parts}
}{}

% 2 - identify_parameter_2

\eoce{\qt{Identify the parameter, Part II\label{identify_parameter_2}} For each of the 
following situations, state whether the parameter of interest is a mean or a 
proportion. 
\begin{parts}
\item A poll shows that 64\% of Americans personally worry a great deal about 
federal spending and the budget deficit.
\item A survey reports that local TV news has shown a 17\% increase in revenue 
within a two year period while newspaper revenues decreased by 6.4\% during this 
time period.
\item In a survey, high school and college students are asked whether or not 
they use geolocation services on their smart phones.
\item In a survey, smart phone users are asked whether or not they use a web-based taxi service.
\item In a survey, smart phone users are asked how many times they used a web-based taxi service over the last year.
\end{parts}
}{}

% 3 - quality_control_ahss

\eoce{\qt{Quality control\label{quality_control_ahss}}
As part of a quality control process for computer chips,
an engineer at a factory samples 212 chips
during a week of production to test the current rate of
chips with severe defects.
She finds that 27 of the chips are defective.
\begin{parts}
\item
    What is the population of interest for the data set?
\item
    What parameter is being estimated?
\item
    What is the value of the point estimator (sample statistic) for the parameter?
\item
   Briefly describe a method that would lead to a biased estimator.  Also, say whether you think the estimator will underestimate or overestimate the parameter.  
\item
    How could you get an unbiased estimator of the parameter?  
\end{parts}
}{}

% 4 - unexpected_expenses_ahss

\eoce{\qt{Unexpected expense\label{unexpected_expenses_ahss}}
In a sample of 765 adults in the United States, 322 say
they could not cover a \$400 unexpected expense without borrowing
money or going into debt.
% Ref: https://www.federalreserve.gov/publications/files/2017-report-economic-well-being-us-households-201805.pdf
\begin{parts}
\item
    What population of interest for the data set?
\item
    What parameter is being estimated?
 \item
    What is the value of the point estimator (sample statistic) for the parameter?
\item
    Briefly describe a method that would lead to a biased estimator.  Also, say whether you think the estimator will underestimate or overestimate the parameter.  
\item
    How could you get an unbiased estimator of the parameter?
\end{parts}
}{}
